### 2015-03-06 supp/supp.tex
modified figure

\begin{figure}
\centering
\includegraphics[width=15cm,height=5.5cm]{simulation_signature_example.eps}
\caption{}
\label{example_signature.pd}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=15cm,height=5cm]{simulation_stat.eps}
\caption{}
\label{example_summary.pd}
\end{figure}

@@

\subfigure[Estimated mutation signatures ($K = 2$)]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K2.eps}
  \label{UTUC:sigK2_sig}}

\subfigure[Estimated mutation signatures ($K = 3$)]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K3.eps}
  \label{UTUC:sigK3_sig}}

\subfigure[Estimated mutation signatures ($K = 4$)]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K4.eps}
  \label{UTUC:sigK4_sig}}

\caption{The result of estimated mutation signatures and membership parameters for UTUC data 
when changing the number of mutation signatures ($K$).}
\label{UTUC_multiK}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=15cm,height=5cm]{UTUC_stat.eps}
\caption{}
\label{example_summary.pd}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=10cm,height=10cm]{UTUC_AA_AAlike_cor.eps}
\caption{}
\label{example_signature.pd}
\end{figure}

@@

% \begin{figure}
% \centering
% \includegraphics[width=15cm,height=15cm]{sig2_group.eps}
% \caption{Mutation signatures obtained for several cancer types categorized as Signature 2}
% \label{example_summary.pd}
% \end{figure}

% \clearpage

% \begin{figure}
% \centering
% \includegraphics[width=15cm,height=3.5cm]{sig6_group.eps}
% \caption{Mutation signatures obtained for several cancer types categorized as Signature 6}
% \label{example_summary.pd}
% \end{figure}

% \clearpage

% \begin{figure}
% \centering
% \includegraphics[width=15cm,height=3.5cm]{sig7_group.eps}
% \caption{Mutation signatures obtained for several cancer types categorized as Signature 7}
% \label{example_summary.pd}
% \end{figure}

% \clearpage

% \begin{figure}
% \centering
% \includegraphics[width=15cm,height=3.5cm]{sig19_group.eps}
% \caption{Mutation signatures obtained for several cancer types categorized as Signature 19}
% \label{example_summary.pd}
% \end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=15cm,height=5.5cm]{simulation_signature_example.eps}
\caption{An example of the relationship between true and estimated mutation signatures in the simulation.
In this example, the numbers of cancer genomes and mutations for each cancer genome are 25 and 100, respectively,
and the parameters $\alpha$ and $\gamma$ are both set to 1. 
From this figure, we can see that fairly accurate estimation is possible even with moderate numbers of cancer genomes and mutations}
\label{example_signature.pd}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=15cm,height=5cm]{simulation_stat.eps}
\caption{The log-likelihood, bootstrap-errors and maximum correlation values among estimated membership parameters for several numbers of signatures $K$ in the trial of the Supplementary Figure 1.}
\label{example_summary.pd}
\end{figure}

@@

\subfigure[$K = 2$]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K2.eps}
  \label{UTUC:sigK2_sig}}

\subfigure[$K = 3$]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K3.eps}
  \label{UTUC:sigK3_sig}}

\subfigure[$K = 4$]{%
  \includegraphics[height=6cm,width=15cm,clip]{UTUC_signature_K4.eps}
  \label{UTUC:sigK4_sig}}

\caption{The result of estimated mutation signatures and membership parameters for UTUC data 
when changing the number of mutation signatures $K$.}
\label{UTUC_multiK}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=15cm,height=5cm]{UTUC_stat.eps}
\caption{The log-likelihood, bootstrap-errors and maximum correlation values among estimated membership parameters for several numbers of signatures $K$ in UTUC data.}
\label{UTUC_stat}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=10cm,height=10cm]{UTUC_AA_AAlike_cor.eps}
\caption{The relationships between the two membership parameters, AA (the first signature in the Supplementary Figure 3) and AA\_like (the second signature in the Supplementary Figure 3) signatures.}
\label{UTUT_AA_AAlike}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=4cm,height=8cm]{UTUC_APOBEC_twoFivePrime.eps}
\caption{The frequencies of bases at two 5' to the mutated site for the APOBEC mutation signatures obtained in UTUC data using the independent and full models.}
\label{UTUC_APOBEC_twoFivePrime}
\end{figure}
